```{r, echo=FALSE, results='hide'}
## source('Users/sarah/Documents/GitHub/landscapes_code/Veg_structure_analysis.R')
source('C://Users/anusha/Documents/GitHub/landscapes_code/nest_data.r')
```

**Title:** Preliminary figures and results from the Hummingbird Monitoring Network nesting structure data
========================================================
**Code & Analysis** 
--------------------------------------
Anusha Shankar, Sarah Supp

**Results**
------------------

This dataset describes hummingbird nest species, location, height; nest tree genus, and nest tree characteristics. The original dataset contains data from Harshaw Creek (HC), Patagonia Lake/Sonoita Creek (PL/SC), The Nature Conservancy (TNC), and El Coronado (EC). However, preliminary analyses were carried out only on HC and PL/SC data.  Data were collected between 29 April, 2013 and 17 July, 2013. A total of `r length(nest$Id)` nests were found and recorded.

**Descriptive graphs**
-------------------

**Figure 1** Number of individuals of each species found nesting at each site.

```{r fig.width=5, fig.height=4, echo=FALSE}
nests_site
```

**Figure 2** Boxplots for nest height at the two sites

```{r fig.width=6, fig.height=4, echo=FALSE}
nest_ht
```

**Figure 3** Genra of trees where nests were found at the two sites

```{r fig.width=6, fig.height=5, echo=FALSE}
nest_trees
```

**Figure 4** Heights of trees where nests were found, at the two sites

```{r fig.width=6, fig.height=5, echo=FALSE}
tree_ht
```

**Figure 5** Status of nests when they were found

```{r fig.width=6, fig.height=5, echo=FALSE}
stage_found
```

**Figure 6** Barplots for nest result at the two sites

```{r fig.width=6, fig.height=5, echo=FALSE}
nest_results
```

**Ststistical analysis** T test looking at difference in nest height between species across sites.

```{r }
report(t.nestht)
```

We still need some clarifications on some of the other variables like Overhead branches- Metadata questions.