```{r, echo=FALSE, results='hide'}
## source('Users/sarah/Documents/GitHub/landscapes_code/Veg_structure_analysis.R')
source('C://Users/anusha/Documents/GitHub/landscapes_code/Veg_structure_analysis.R')
```

**Title:** Preliminary figures and results from the Hummingbird Monitoring Network Vegetation structure data
========================================================
**Code & Analysis** 
--------------------------------------
Sarah R. Supp, Anusha Shankar, Tina Cormier

**Results**
------------------
We split the vegetation structure dataset into its multiple components: Trees, shrubs, canopy, and ground cover. Data were collected between 8 July, 2013 and 16 July, 2013. Here we compare canopy cover, ground cover, shrub sizes and species, and tree sizes and species across and between sites.

**Descriptive graphs**
-------------------

**Figure 1** Densitometry by site. This refers to total proportion of sky covered by canopy + subcanopy + bare branches.

```{r fig.width=3, fig.height=4, echo=FALSE}
densitometry_site
```

**Figure 2** Canopy cover by site. ############ Need to work on this

```{r fig.width=6, fig.height=4, echo=FALSE}
cc_site_box
```

**Figure 3** Ground cover by site. Proportion of ground covered by different materials.

```{r fig.width=6, fig.height=5, echo=FALSE}
ground_site
```

**Figure 4** Height of trees by genus and site.

```{r fig.width=6, fig.height=5, echo=FALSE}
tree_genus_height
```

**Figure 5** Height of trees by genus and site.

```{r fig.width=6, fig.height=5, echo=FALSE}
tree_genus_height
```

**Figure 6** Canopy radius by tree genus

```{r fig.width=6, fig.height=5, echo=FALSE}
tree_genus_canopy
```

**Figure 7** Tree dbh by genus and site. Class 1: 2-4 cm; Class 2: 5-20 cm; Class 3: 20-30 cm; Class 4: >= 30 cm

```{r fig.width=6, fig.height=5, echo=FALSE}
tree_genus_dbh
```

**Differences between sites**
-----------------------
**Figure 8** Tree height by site.

```{r fig.width=6, fig.height=5, echo=FALSE}
tree_site_height
```

**Figure 9** Canopy radius by site.

```{r fig.width=6, fig.height=5, echo=FALSE}
tree_site_canopy
```

**Figure 10** Tree dbh by site. Class 1: 2-4 cm; Class 2: 5-20 cm; Class 3: 20-30 cm; Class 4: >= 30 cm.

``` {r fig.width=6, fig.height=5, echo=FALSE}
tree_site_dbh
```

**Figure 11** Shrub size by site.

``` {r fig.width=6, fig.height=5, echo=FALSE}
shrub_site_size
```
